TacticToe: Learning the Game of Tactics

### 2018-02-15 tactictoe_jv.tex
minor

\begin{example}\label{ex:cs4}
\begin{lstlisting}[language=SMLSmall]
count (n+m) DIFF count n = IMAGE ((+) n) (count m)
SRW_TAC [ARITH_ss] [fetch "pred_set" "EXTENSION", EQ_IMP_THM] THEN
Q.EXISTS_TAC `x - n` THEN
SRW_TAC [ARITH_ss] []
\end{lstlisting}
\end{example}

>>>>

\begin{example}\label{ex:cs4}
\begin{lstlisting}[language=SMLSmall]
count (n+m) DIFF count n = IMAGE ((+) n) (count m)
SRW_TAC [ARITH_ss] [EXTENSION, EQ_IMP_THM] THEN
Q.EXISTS_TAC `x - n` THEN
SRW_TAC [ARITH_ss] []
\end{lstlisting}
\end{example}
